Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-22 paper/paper.tex
Finish 7th page

More specifically, we computed the following numbers for the tickets we collected:
\begin{itemize}
  \item out of the 303,138 tickets, 236,383 tickets were closed (i.e. marked Closed, Resolved, Done or Completed) by the time we 
  fetched them from the Jira instance;
  \item 287,120 tickets are of high priority (i.e. marked as Blocker, Critical, Major or High);
  \item 201,786 tickets have all our requirements for running the analysis: were closed by the time we fetched the data, 
  are of high priority and are not \emph{wrong} values retrieved from Jira (i.e. outliers);
  \item 103,397 tickets have attachments which we split in the following categories:
    \begin{itemize}
      \item 4,082 have code attachments (e.g. Go, Java, Python);
      \item 7,171 have image attachments (e.g. png, jpg/jpeg, gif);
      \item 164 have video attachments (e.g. mkv, avi, mp4);
      \item 13,990 have text attachments (e.g. txt, md, doc(x));
      \item 918 have config attachments (e.g. json, xml, yml);
      \item 2,491 have archive attachments (e.g. zip, tar.gz, rar, 7z);
      \item 280 have spreadsheet attachments (e.g. csv, xlsx);
      \item 80,015 have other attachments (i.e. any file extension not pre-defined by us in one of the above categories).
    \end{itemize}
  \item 270,907 tickets have comments;
  \item 39,988 tickets have steps to reproduce (i.e. sequence of steps specified by the bug reporter that would reproduce a certain bug); 
  we applied the general guidelines described by Bettenburg et al. \cite{bettenburg2008extracting} on how to extract structured 
  data (including steps to reproduce) from tickets in order to create a regular expression for capturing them;
  \item 1,942 tickets have Java stack traces - we applied the technique described by Bettenburg et al. 
  \cite{bettenburg2008extracting} for extracting structured data from bug reports;
  \item 133,689 tickets have grammar correctness scores (i.e. number of grammar mistakes inside summary, description and comments) - 
  they were computed using Microsoft Azure Bing Spell Check API which is one of the best grammar checking tool in the industry; 
  \item 157,047 tickets have sentiment scores (i.e. positive/negative sentiment on a scale from -1 to 1 drawn from summary, description
  and comments) - they have been collected using Google Cloud Platform Natural Language Processing APIs.
\end{itemize}

All these numbers are also stored inside the database in a different bucket for easier access in the future. Moreover, the statistical 
tests we ran on the tickets are saved as well in the database.

@@

In this section we present our results to the research questions we set to answer. We have computed charts for all 
independent variables using either scatter plots for continuous variables (e.g. number of comments/\emph{Time-To-Close}) 
or bar charts for categorical variables (e.g. presence of attachments). We also computed statistical analysis for 
all variables to test their significance and rank correlation coefficient and we will present each of them in their 
corresponding subsection.

The answers to our research questions are all statistically significant and they can summarised as follows:
\begin{itemize}
  \item having attachments reduces \emph{Time-To-Close} of a ticket;
  \item having steps to reproduce reduces \emph{Time-To-Close} of a ticket;
  \item having stack traces reduces \emph{Time-To-Close} of a ticket;
  \item more grammar errors imply increase \emph{Time-To-Close} values;
  \item lower sentiment scores result in increased \emph{Time-To-Close} values;
  \item verbose comments result in increased \emph{Time-To-Close} values;
  \item verbose summary and description imply increased \emph{Time-To-Close} values.
\end{itemize}

@@

Attachments are, as mentioned previously, files attached to software tickets that can take any form - from code 
snippets written in Java to tar archives. We have analyzed all tickets that were both of high priority tickets and
were marked as Closed by the time we collected the data. Then we split all these tickets into two main categories: 
with attachments and without attachments. Furthermore, the tickets that were marked as having attachments were split 
into the categories specified in Section \ref{characterising}. In total, we looked at 201,786 tickets, among which 
98,311 had attachments and 103,475 without any attachments.

Using the plot package in our Go tool, we automatically generated the bar chart shown in Figure \ref{attachments}. 
As it can be seen, various types of attachments can produce completely different \emph{times-to-close}. For 
tickets with archive we can see the longest \emph{Time-To-Close} mean while tickets having text attachments are at 
the other end of the spectrum. The smallest mean is for other attachments, which is represented by any file 
that does not have an extension specified in one of the other categories.

@@

Another insightful result is the fact that having text, config and spreadsheet attachments significantly 
reduces the \emph{Time-To-Close} for the ticket. This can imply that developers find value in various steps to reproduce, 
config values used by users when the bug encountered or data in a spreadsheet format (e.g. csv) that can be 
found in such files and helps them lower the \emph{Time-To-Close} for the ticket.

@@

However, we need to take into consideration tickets that have code attachments which are a \emph{thread to validity}. 
When a snippet of code is attached, it might result in more complex tickets due to developers spending more time on 
understanding what is going on and reasoning about the attached code. Also, engineers might need to run or test 
the code attached which can again increase the Time-To-Close.

A Welch T Test was computed to test the difference between tickets with attachments and those 
without attachments. The analysis revealed significant difference with $p > 0.01$ with an
average of $1380.551$ hours for tickets with attachments and an average of $3180.882$ hours
for tickets without attachments.

Thus, our analysis shows that having attachments in most formats, ranging from markdown files to PNG screenshots 
and snippets of code, can help developers solve the tickets faster. We believe that the solution of making attachments
provide the most value to the software project would be if issue tracking systems would make explicit to the reporters 
that uploading a screenshot or a code snippet can help reduce the \emph{Time-To-Close} for the ticket.

>>>>

More specifically, we computed the following numbers for the tickets we collected:
\begin{itemize}
  \item out of the 303,138 tickets, 236,383 tickets were closed (i.e. marked Closed, Resolved, Done or Completed) by the time we 
  fetched them from the Jira instance;
  \item 287,120 tickets are of high priority (i.e. marked as Blocker, Critical, Major or High);
  \item 201,786 tickets have all our requirements for running the analysis: were closed by the time we fetched the data, 
  are of high priority and are not \emph{wrong} values retrieved from Jira (i.e. outliers);
  \item 103,397 tickets have attachments which we split in the following categories:
    \begin{itemize}
      \item 4,082 have code attachments (e.g. Go, Java, Python);
      \item 7,171 have image attachments (e.g. png, jpg/jpeg, gif);
      \item 164 have video attachments (e.g. mkv, avi, mp4);
      \item 13,990 have text attachments (e.g. txt, md, doc(x));
      \item 918 have config attachments (e.g. json, xml, yml);
      \item 2,491 have archive attachments (e.g. zip, tar.gz, rar, 7z);
      \item 280 have spreadsheet attachments (e.g. csv, xlsx);
      \item 80,015 have other attachments (i.e. any file extension not pre-defined by us in one of the above categories).
    \end{itemize}
  \item 270,907 tickets have comments;
  \item 39,988 tickets have steps to reproduce (i.e. sequence of steps specified by the bug reporter that would reproduce a certain bug); 
  we applied the general guidelines described by Bettenburg et al. \cite{bettenburg2008extracting} on how to extract structured 
  data (including steps to reproduce) from tickets in order to create a regular expression for capturing them;
  \item 1,942 tickets have Java stack traces - we applied the technique described by Bettenburg et al. 
  \cite{bettenburg2008extracting} for extracting structured data from bug reports;
  \item 133,689 tickets have grammar correctness scores (i.e. number of grammar mistakes inside summary, description and comments) - 
  they were computed using Microsoft Azure Bing Spell Check API which is one of the best grammar checking tool in the industry; 
  \item 157,047 tickets have sentiment scores (i.e. positive/negative sentiment on a scale from -1 to 1 drawn from summary, description
  and comments) - they were calculated using Google Cloud Platform Natural Language Processing APIs.
\end{itemize}

All these numbers are also stored inside the database in a different bucket for easier access in the future. Moreover, the statistical 
tests that were run on the tickets are saved as well in the database.

@@

In this section we present our results to the research questions we set to answer. We computed charts for all 
independent variables using either scatter plots for continuous variables (e.g. number of comments/\emph{Time-To-Close}) 
or bar charts for categorical variables (e.g. presence of attachments/\emph{Time-To-Close}). We also computed statistical analysis for 
all variables to test their significance and rank correlation coefficient and we will present each of them in their 
corresponding subsection.

The answers to our research questions are all statistically significant and they can be summarised as follows:
\begin{itemize}
  \item having attachments reduces \emph{Time-To-Close} of a ticket;
  \item having steps to reproduce reduces \emph{Time-To-Close} of a ticket;
  \item having stack traces reduces \emph{Time-To-Close} of a ticket;
  \item more grammar errors increase \emph{Time-To-Close} values;
  \item lower sentiment scores result in increased \emph{Time-To-Close} values;
  \item verbose comments result in increased \emph{Time-To-Close} values;
  \item verbose summary and description increase \emph{Time-To-Close} values.
\end{itemize}

@@

Attachments are, as mentioned previously, files attached to software tickets that can take any form - from code 
snippets written in Java to tar archives. We analysed all tickets that were both of high priority and
were closed by the time we had collected the data. Then we split all these tickets into two main categories: 
with attachments and without attachments. Furthermore, the tickets that were marked as having attachments were split 
into the categories specified in Section \ref{characterising}. In total, we looked at 201,786 tickets, among which 
98,311 had attachments and 103,475 without any attachments.

Using the plot package in our Go tool, we automatically generated the bar chart shown in Figure \ref{attachments}. 
As it can be seen, various types of attachments produce completely different \emph{times-to-close}. For 
tickets with archive we can see the longest \emph{Time-To-Close} mean while tickets with text attachments are at 
the other end of the spectrum. The smallest mean is for other attachments, which is represented by any file 
that does not have an extension specified in one of the other categories.

@@

Another insightful result is the fact that having text, config and spreadsheet attachments significantly 
reduces the \emph{Time-To-Close} for the ticket. For example, when a config file is present, it might contain 
several environment variables that would help developers recreate the bug quicker. Similarly, a markdown file 
might have logging output which potentially directs engineers towards fixing the issue faster.

@@

However, we need to take into consideration tickets that have code attachments which are a \emph{threat to validity}. 
When a snippet of code is attached, it might result in more complex tickets due to developers spending more time on 
understanding what is going on and reasoning about the attached code. Also, engineers might need to run or test 
the code attached which can again increase the Time-To-Close.

A Welch T Test was computed to test the difference between tickets with attachments and those 
without attachments. The analysis revealed significant difference with $p < 0.01$ with an
average of $1380.551$ hours for tickets with attachments and an average of $3180.882$ hours
for tickets without attachments.

Thus, our analysis shows that having attachments in most formats, ranging from markdown files to PNG screenshots 
and snippets of code, can help developers solve the tickets faster. We believe that a solution to maximising the value 
of a ticket through attachments lies in issue tracking systems making it explicit to the reporters that uploading a screenshot 
or a code snippet could help reduce the \emph{Time-To-Close} for the ticket.
